### 2022-11-28 ms.rmd
Ok, you need to remember that these are BLUPS, deviations form intercept (duh) so one needs to add in the mean intercept.

# Extract the estimated / imputed Z for each species, but drop internal ancestral nodes
  z <- sol[, grep("traittdt_z.animal", colnames(sol))]
  z <- z[,-grep("Node", colnames(z))]
  head(z)

>>>>

# Extract the estimated / imputed Z for each species, but drop internal ancestral nodes
  z_blups <- sol[, grep("traittdt_z.animal", colnames(sol))]
  z_blups <- z[,-grep("Node", colnames(z))]
  head(z_blups)

# Remember that these are BLUPs. They are deviations from the intercept. So, to get back to the z we need to add the intercept to each of them.
  z <- z_blups + mean(sol[, "traittdt_z"])
